### 2024-06-05 draft.qmd
20240604 - bullets
20240604 - edit

    - your [player evaluation](player-evaluation.qmd)
    - expert or aggregated rankings
    - players' Average Draft Position (ADP) in other league drafts (for snake drafts), or players' Average Auction Value (AAV) in other league drafts (for auction drafts)
    - expert or aggregated projections

>>>>

- your [evaluation of players](player-evaluation.qmd)
- expert or aggregated rankings
- players' Average Draft Position (ADP) in other league drafts (for snake drafts), or players' Average Auction Value (AAV) in other league drafts (for auction drafts)
- expert or aggregated projections
